### 2015-10-07 paper-1/main.tex
Updated the kplot based on Dan's feedback.

The maxiumu sample size is 12 but the number of patients necessary to 
reach and endpoint can be less. Our goal is to describe the distribution of 
the enrollment size of the design for 
planning purposes and to use this distribution to estimate the
success probability.  If all 12 patients are enrolled at once, 
as in the classic 
design, then the sample size is 12. However, in most clinical trials, the 
patients are enrolled sequentially, often with one patient's outcome realized 
before the next one enters the trial. In the present example, observing two 
successful patients allows us to proceed to the next stage. Similarly 11 
observed treatment failures also ends the stage. This sampling mechanism, in 
which the experiment ends as soon as any of the endpoints is reached, is 
call {\em curtailed sampling}. Under curtailed sampling the range of the 
sample size is between two and 12.

We assume each of the patient outcomes can be modeled as independent, 
identically distributed Bernoulli($p$) random variables. The realization of 
the trial is a sequence of these random variables that stops when either a 
specified number of success or failures is reached. As in the 
previous example, two successes were reached after enrolling 10 
patients (one in the third step and one at the $10^{th}$). The trial is 
visualized in Fig.~\ref{fig:kane_viz}. The vertical axis denotes the number of 
successful outcomes. The horizontal axis denotes the number of patients that 
have been enrolled. The horizontal and vertical line segments represent 
boundayr endpoints for the trial.

@@

To show the result in Eqn.~\ref{eqn:pmf} consider the 
process $\mathbf{X} = \{X(k) : k \in \mathbb{Z}_{\ge 0} \}$ with $X(0)=0$ and
\begin{equation*} \label{eqn:proc}
X_{k+1} = X_k + b_{k+1} \left[ k-t < X_k < s \right].
\end{equation*}
As before the $b_{k+1}$'s are distributed as Bernoulli($p$) for all $k$ in the 
domain of $\mathbf{X}$. The process can be conceptualized as a series of coin 
flips that stops when either $s$ heads or $t$ tails are reached. At each step 
a coin is flipped. If it is heads, the process advances one diagonally in the 
positive horizontal and vertical direction. Otherwise, it advances in the 
positive horizontal direction only. When the process stops
either $X_k = s$ or $X_k = k-t$. One example is given in 
Fig.~\ref{fig:kane_viz}.

@@

The probability that a given realization of $\mathbf{X}$ reaches $s$ at 
the $k$th outcome is the probability that, at time $k-1$ there are $s-1$ 
successful outcomes and $k-s$ unsuccessful outcomes multiplied by 
the probability of a 
success at time $k$ (\ref{eqn:N}). The probability $X_k = k-t$ 
is the probability that, at outcome $k-1$ there are $k-t$ successful outcomes 
and $t-1$ unsuccessful outcomes multiplied by the probability of an 
unsuccessful outcome at time $k$ (\ref{eqn:R}).  Finally, we need to show that 
the sum
\begin{equation} \label{eqn:sum_proof}
R = \sum_{k=s}^{s+t-1} {k-1 \choose s-1} p^s (1-p)^{k-s} + \sum_{k=t}^{s+t-1} {k-1 \choose k-t} p^{k-t} (1-p)^t
\end{equation}
is equal to one.
First, substitute $i=k-s$ in the first summation and
$j=k-t$ in the second. 
\begin{equation*}
{j+s-1 \choose s-1} = {j+s-1 \choose j}
\end{equation*}
Then %(\ref{eqn:sum_proof}) becomes:
%\begin{equation*}
%R = \sum_{i=0}^{t-1} {i+s-1 \choose s-1} p^s (1-p)^i +
%\sum_{j=0}^{s-1} {j+t-1 \choose j} p^j (1-p)^t.
%\end{equation*}
$R$ can be written
as the cumulative distribution function of two 
negative binomial distributions
\begin{equation} \label{eqn:transformed_sum}
R = \sum_{i=0}^{t-1} {i+s-1 \choose i} p^s (1-p)^i \; + \;
\sum_{j=0}^{s-1} {j+t-1 \choose j} p^j (1-p)^t.
\end{equation}

>>>>

The maximum sample size is 12 but the number of patients necessary to 
reach and endpoint can be less. Our goal is to describe the distribution of 
the enrollment size of the design for 
planning purposes and to use this distribution to estimate the
success probability.  If all 12 patients are enrolled at once, 
as in the classic 
design, then the sample size is 12. However, in most clinical trials, the 
patients are enrolled sequentially, often with one patient's outcome realized 
before the next one enters the trial. In the present example, observing two 
successful patients allows us to proceed to the next stage. Similarly 11 
observed treatment failures also ends the stage. This sampling mechanism, in 
which the experiment ends as soon as any of the endpoints is reached, is 
call {\em curtailed sampling}. Under curtailed sampling the range of the 
sample size is between two and 12.

We assume each of the patient outcomes can be modeled as independent, 
identically distributed Bernoulli($p$) random variables. The realization of 
the trial is a sequence of these random variables that stops when either a 
specified number of success or failures is reached. As in the 
previous example, two successes were reached after enrolling 10 
patients (one in the third step and one at the $10^{th}$). The trial is 
visualized in Fig.~\ref{fig:kane_viz}. The vertical axis denotes the number of 
successful outcomes. The horizontal axis denotes the number of patients that 
have been enrolled. The horizontal and vertical line segments represent 
boundary endpoints for the trial.

@@

To show the result in Eqn.~\ref{eqn:pmf} consider the 
process $\mathbf{X} = \left[X(k) : k \in \mathbb{Z}_{\ge 0} \right]$ 
with $X(0)=0$ and
\begin{equation*} \label{eqn:proc}
X_{k+1} = X_k + b_{k+1} \left[ k-t < X_k < s \right].
\end{equation*}
As before the $b_{k+1}$'s are distributed as Bernoulli($p$) for all $k$ in the 
domain of $\mathbf{X}$. The process can be conceptualized as a series of coin 
flips that stops when either $s$ heads or $t$ tails are reached. At each step 
a coin is flipped. If it is heads, the process advances one diagonally in the 
positive horizontal and vertical direction. Otherwise, it advances in the 
positive horizontal direction only. When the process stops
either $X_k = s$ or $X_k = k-t$. One example is given in 
Fig.~\ref{fig:kane_viz}.

@@

The probability that a given realization of $\mathbf{X}$ reaches $s$ at 
the $k$th outcome is the probability that, at time $k-1$ there are $s-1$ 
successful outcomes and $k-s$ unsuccessful outcomes multiplied by 
the probability of a 
success at time $k$ (\ref{eqn:N}). The probability $X_k = k-t$ 
is the probability that, at outcome $k-1$ there are $k-t$ successful outcomes 
and $t-1$ unsuccessful outcomes multiplied by the probability of an 
unsuccessful outcome at time $k$.  Finally, we need to show that 
the sum
\begin{equation} \label{eqn:sum_proof}
R = \sum_{k=s}^{s+t-1} {k-1 \choose s-1} p^s (1-p)^{k-s} + \sum_{k=t}^{s+t-1} {k-1 \choose k-t} p^{k-t} (1-p)^t
\end{equation}
is equal to one.
First, substitute $i=k-s$ in the first summation and
$j=k-t$ in the second. 
\begin{equation*}
{j+s-1 \choose s-1} = {j+s-1 \choose j}
\end{equation*}
Then %(\ref{eqn:sum_proof}) becomes:
%\begin{equation*}
%R = \sum_{i=0}^{t-1} {i+s-1 \choose s-1} p^s (1-p)^i +
%\sum_{j=0}^{s-1} {j+t-1 \choose j} p^j (1-p)^t.
%\end{equation*}
$R$ can be written
as the cumulative distribution function of two 
negative binomial distributions
\begin{equation} \label{eqn:transformed_sum}
R = \sum_{i=0}^{t-1} {i+s-1 \choose i} p^s (1-p)^i \; + \;
\sum_{j=0}^{s-1} {j+t-1 \choose j} p^j (1-p)^t.
\end{equation}
